Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-04-09 pkg/disttree/inst/draft/draft.Rnw
small corrections
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2139 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 3dbb05a0185a04b39327a106aa37a18860b620d5

<<plot_motivation_disttree, fig=TRUE, echo=FALSE>>=
par(mar = c(2, 0, 2, 0))
plot(x, y, xaxt="n", yaxt="n", ann=FALSE, type = "n")
usr <- par("usr")
rect(usr[1], usr[3], usr[2], usr[4], col = gray(0.94), border = "transparent")
lines(x = x, y = ytree, col = pal[1], lwd=7, main = "")
polygon(c(x, rev(x)), c(ytree + var, rev(ytree - var)),
  col = pallight[1], border = "transparent")
points(x, y, col = "slategray", pch = 19)
box(lwd=8)
@
\vspace{-0.2cm}%\\
Distributional tree
\vspace{0.2cm}
\endminipage};
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](2.1,0)--(2.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=0.9pt](7.1,0)--(7.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=0.9pt](0,-2.4)--(0,-3.2);
\draw[-{>[scale=4, length=2, width=3]},line width=0.9pt](2.2,-5.4)--(7.9,-2.5);
\end{tikzpicture}
\caption{\label{fig:tree}Tree and forest developments.
Regression tree (top left), distributional tree (bottom left), random forest
(top middle), and distributional forest (top right).}
\end{figure}

>>>>

<<plot_motivation_disttree, fig=TRUE, echo=FALSE>>=
par(mar = c(2, 0, 2, 0))
plot(x, y, xaxt="n", yaxt="n", ann=FALSE, type = "n")
usr <- par("usr")
rect(usr[1], usr[3], usr[2], usr[4], col = gray(0.94), border = "transparent")
lines(x = x, y = ytree, col = pal[1], lwd=7, main = "")
polygon(c(x, rev(x)), c(ytree + var, rev(ytree - var)),
  col = pallight[1], border = "transparent")
points(x, y, col = "slategray", pch = 19)
box(lwd=8)
@
\vspace{-0.2cm}%\\
Distributional tree
\vspace{0.2cm}
\endminipage};
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](2.1,0)--(2.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](7.1,0)--(7.9,0);
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](0,-2.4)--(0,-3.2);
\draw[-{>[scale=4, length=2, width=3]},line width=0.4pt](2.2,-5.4)--(7.9,-2.5);
\end{tikzpicture}
\caption{\label{fig:tree}Tree and forest developments.
Regression tree (top left), distributional tree (bottom left), random forest
(top middle), and distributional forest (top right).}
\end{figure}
